Slitasje og kjørespor

### 2022-11-29 DRAFT_slitasjeOgKjørespor.Rmd
GRUK

This variable is also recorded in GRUK

@@

```{r}
tm_shape(soner)+
  tm_polygons(col = "NAVN")
```

It could make sense to combine some zones, but I will later split the sones by region, and then merge sones that are very uncommon in a spesific region.

>>>>

This variable is also recorded in GRUK. The nature type dataset I'm working on here includes this data already (presently only 2021 included). GRUK also records a related variable: % cover in 5m radii circles. This data is not published.In any case it is better to use the harmonized dataset.

@@

```{r}
tm_shape(soner)+
  tm_polygons(col = "NAVN",
              title = "Vegetation zone")
```

It could make sense to combine some zones, but I will later split the zones by region, and then merge sones that are very uncommon in a spesific region.
